Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-02 manuscript.Rmd
Update CRPs to have event-specific coloring

# specify global plotting variables for easier testing
all_event_color = "#CC79A7"
positive_event_color = "#0072B2"
negative_event_color = "#D55E00"
line_thickness = 2

>>>>

# specify global plotting variables
all_event_color = "#CC79A7"
positive_event_color = "#0072B2"
negative_event_color = "#D55E00"
line_thickness = 2
